% QUESTION N
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Question N:\\Islands}

\subsection{Description}
Vangelis the bear is the proud owner of a swamp that is composed by several 
small islands. He really likes his swamp but he hates swimming. In order 
to allow himself to enjoy his islands, he decided to build connection paths 
that connect those islands together.

Vangelis has at his disposal a map of the swamp. This map is a square grid 
with dimensions NxN (where N is greater than 1 \& less than or equal to 1000) 
and is composed by squares that are either black or white. A black color 
square represents a piece of land and a white one an area of water. 
Two black squares are said to be connected if they are directly adjacent 
in the horizontal or vertical direction (not in the diagonal direction). 
We define an island as a set of one or more black squares such that each 
black square in the island is connected to at least one other black 
square in the island.

\subsection{Task}
Your task is to determine how many white squares need to be converted to 
black squares so that there will be only one island in the diagram with 
the least amount of conversions. Most test cases will have more than 
one solution.

\subsection{Input}
Your program should read the standard input. The first line of the input 
contains the integer N. Each of the following N lines contains N numbers 
on each line. The numbers on each line are either a 0 or a 1, separated 
by a single space. A 1 represents a black square, and a 0 represents 
a white square.

\subsection{Output}
Your program should write on the standard output a number M, the number 
of white squares to be converted to black.Note: There is no new line 
character at the end of the result.

\subsection{Input 1}
10\\
0 0 0 0 0 0 0 0 0 0\\
0 0 0 0 0 0 0 0 0 0\\
0 0 0 0 0 0 0 0 0 0\\
0 0 0 0 0 0 0 0 0 0\\
1 0 0 0 0 0 0 0 0 1\\
0 0 0 0 0 0 0 0 0 0\\
0 0 0 0 0 0 0 0 0 0\\
0 0 0 0 0 0 0 0 0 0\\
0 0 0 0 1 0 0 0 0 0\\
0 0 0 0 0 0 0 0 0 0

\subsection{Output 1}
11\\
 
\subsection{Input 2}
2\\
1 0\\
0 1\\

\subsection{Output 2}
1\\
 
\subsection{Input 3}
4\\
1 0 0 0\\
0 0 0 0\\
0 0 0 0\\
0 0 0 1\\

\subsection{Output 3}
5

