% QUESTION V
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Question V:\\Hogwart's Cup}

\subsection{Description}
It’s almost the end of the year; Dumbledore wants to give out 
the Hogwarts House cup to the group that has the most points. 
However recent events need to be considered and he has some 
last minute points to be awarded. Dumbledore could wave his wand 
to find the winner, but a critical bug in the wand's code 
made it to stop working. You need to help him, calculate the 
revised scores of each of the group and announce the highest score. 
Dumbledore is counting on you.

\subsection{Input Format}
First line is the number of Test Cases, N.

Next line contains Number of students X (X <= 100000), 
Number of Revision operations R, Number of Group values to 
calculate G.(\#R + \#G <= 100000)

Next line will be the initial scores for each of the students. 
Space separated s1..sX. Each student can be awarded a 
maximum score of 100.

Next line will continue with operations for score revision. 
Line starts with R, next value is the index of student to 
revise, and next value is the extra points awarded.

Further down will be the operations for calculating 
group totals. Group start student index, and end student 
index. (Both students inclusive)

\subsection{Output Format}
Highest score of the entire group score calculations

Note: There is no new line character at the end of the result.

\subsection{Test Input}
1\\
10 2 2\\
1 1 1 1 1 1 1 1 1 1\\
R 2 2\\
R 8 3\\
G 1 6\\
G 5 10\\

\subsection{Test Output}
9
