% QUESTION X
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Question X:\\Hacker's Challenge}

\subsection{Description}
You are part of your national security team who is trying to 
breakdown on the plans of a terrorist group. Everybody has 
high hopes on you to obtain the magic key that will open all 
the enemy secrets, your other team mates have been successful 
in tricking the enemy to dip his hands in invisible radium 
ink after which he typed the secret key to unlock his precious 
computer. The intelligence has also found that the key is might 
be one among the standard words of a secret dictionary(which they 
have managed to sniff out from the enemies). Your counterparts have 
done their job, now its upto you. Being a terrific programmer, the 
team expects you to give them a list of probable keys which they can 
use to unlock the computer. So, you have the list of characters which 
is part of the key and the dictionary, return the list of keys as
soon as possible. If you don't find any possible keys then there 
is a mole in your team!

\subsection{Input}
First line will have a number n, the number of words in dictionary. 
$1<=n<=2*10^5$.
Followed by exactly 'n' words(separated by whitespace, each word 
at max having 100 charcters - only small case).
Next line will have number of testcases, t. $1<=t<=10^3$.
't' lines follow each with a set of characters(without any spaces, 
max length of 26 - only small case) which forms the key.

\subsection{Output}
For each test case, print a line with list of all the words, 
separated by space, which might be probable keys in sorted order. 
If there is no key matching then print "NONE" (quotes are only for clarity).

\subsection{Example Input}
10\\
bill ilp lip pile pill tout out lipp cool dude\\
2\\
ilp\\
blyah

\subsection{Example Output}
ilp lip lipp pill\\
NONE
